Why, when and how to latent mean center variables in multilevel models

### 2022-11-23 ms.Rmd
Manuscript structure?
Name typo

@@

We would like to thank Mauricio Garnier-Villarre, Simon Brauer, Ethan McCormick, and everyone else who contributed to the discussion and development of the correct brms syntax on the Stan discussion board (https://discourse.mc-stan.org/t/latent-mean-centering-latent-covariate-models-in-brms/29424). Special thanks to Mauricio Garnier-Villarre for being the first to post the syntax that the code here was based on. We believe developing methods and theories collaboratively, and in the open, to be a fruitful path forward in better understanding human behavior and how to best model it.

>>>>

# Introduction

## Centering

## Latent mean centering

# Example analysis

# Simulation study

# Discussion

@@

We would like to thank Mauricio Garnier-Villarre, Simon Brauer, Ethan McCormick, and everyone else who contributed to the discussion and development of the correct brms syntax on the Stan discussion board (https://discourse.mc-stan.org/t/latent-mean-centering-latent-covariate-models-in-brms/29424). Special thanks to Mauricio Garnier-Villarre for being the first to post the syntax that the code here was based on. We believe developing methods and theories collaboratively, and in the open, to be a fruitful path forward in better understanding human behavior and how to best model it.
We would like to thank Mauricio Garnier-Villarreal, Simon Brauer, Ethan McCormick, and everyone else who contributed to the discussion and development of the correct brms syntax on the Stan discussion board (https://discourse.mc-stan.org/t/latent-mean-centering-latent-covariate-models-in-brms/29424). Special thanks to Mauricio Garnier-Villarreal for being the first to post the syntax that the code here was based on. We believe developing methods and theories collaboratively, and in the open, to be a fruitful path forward in better understanding human behavior and how to best model it.
